Openness and computational reproducibility in plant pathology: where do we stand and a way forward

### 2022-10-14 analysis/paper/paper.Rmd
Reword results of analysis

There was no detectable effect or non-effect for year when predicting the availability of computational methods (Figure \@ref(fig:year-parameters)A, Table S3, Figure S4).
However, the year of publication did not have an effect on the availability of data (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).

>>>>

There was no clear effect for year when predicting the availability of computational methods (Figure \@ref(fig:year-parameters)A, Table S3, Figure S4).
However, the year of publication did not have an effect on the availability of data (Figure \@ref(fig:year-parameters)B, Table S4; Figure S5).
